A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness

### 2019-05-01 Paper_neural_coarse_graining_of_consciousness.tex
Update from local

				@ \rewrite{
					It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig. 3, but the brain has no direct access to visual stimuli except that provided by the retina. Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs? More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + Δ t in the future? The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +Δ t j w t Þ } \url{http://tinyurl.com/y9zmhlln}

@@

		\subsection{Informational closure and level identification \ideaCallout{maybe not necessary}}

		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}

@@

\rlstart{3}	
		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
	    \ideaBox{I need to expend this section much more and more references}
	    In this section, we suggest that our theory has a strong exploratory and predictive power but with minimal assumptions.  
		Our theory indicates that to make information conscious two necessary conditions need to be satisfied with in any system.

		\begin{enumerate}
		    \item Information is encoded in NTIC process. 
		    \item The system is capable of constructing NTIC processes at coarse-grained levels. 
		\end{enumerate}

@@

		    @ Boundary 
    		    @@ binocular rivalry/CFS
    		    @@ Libet's experiment
    		    @@ Priming
    		    @@ Bistable perception
    		    @@ Perceptual overflow
    		    @@ Unconscious determinants of free decisions in the human brain
    		    @@ Threshold of unconscious to consciousness
    		    @@ Probabilistic information is always unconscious

@@

			\begin{WritingMaterials}
				@ \rewrite{
					The ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations. Thus the crucial difference between the ﬁrst-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity. Therefore, in the group of ﬁrst-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the ﬁrst-order representations, as well as scientists who hold that visual awareness depends on activity in content-speciﬁc regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26]. Most ﬁrst-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g. subcortical) sensory pathways. Thus this view suggests that conscious and unconscious processing will have different functional consequences. Whereas some ﬁrst-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most ﬁrst-order theorists take a difference in perceptual task performance (e.g. ‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33]. In other words, they typically associate task performance with awareness..} \cite{lau2011empirical}

@@

			@ \rewrite{
				neutral about whether conscious awareness adds signiﬁcant utility or immediate impact on behavior and task performance [1,27]. This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on ﬁrst-order rather than higher-order representations. Because conscious awareness can differ even if all ﬁrst-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
				\ideaCallout{
					My theory would have similar prediction. Because conscious contents are coarse-grained results from low-level information. It is possible that more than two low-level neural states all coarse-grained to a high-level state.  }

			@ \rewrite{
					Metacognition: cognition that is about another cognitive process as opposed to about objects in the world. In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efﬁcacy of a perceptual process. The capacity of sensory metacognition is sometimes empirically assessed by the correspondence between subjective report and task performance: how closely are they associated with each other on a trial-by-trial basis}\cite{lau2011empirical}

@@

		Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates. In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process. This can cause a significant change of the brain states and resembles non-linear ignition of brain activities. Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing? Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness. A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly deﬁned brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ]. Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed. \todo{Cite similar opinion from other theories}

@@

					@ e ‘all-or-none’ behavior, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and ampliﬁed non-linearly into a full-blown state of high-level activity. This global ‘ignition’ has been proposed as a marker of conscious perception [70]. Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear ampliﬁcation of activation which invades a distributed set of parietal, prefrontal and cingulate areas
				\end{WritingMaterials}

@@

			\subsubsection{Ignition}
				\begin{WritingMaterials}
					@ Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing? Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness. A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly deﬁned brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ]. Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed. 
				\end{WritingMaterials}

@@

				@ In their seminal article O’Regan and Noe¨ (2001) introduce sensorimotor contingencies (SMCs) as the basis of a sensorimotor account of conscious perception.

@@

				@ The second variant of SMC theory postulates that ‘ it is not movement as such, but the consequences of potential movement that play a role ’ (in perceptual experience) ([5], p. 1015; see also [9,10,19,20]). This ‘ non-acute ’ or dispositional variant marks a signi ﬁ cant shift in position because it de-emphasizes actual movement. \cite{pennartz2017consciousness}

@@

					@@ However, these authors have so far been very reticent about how exactly consciousness ﬁts into the PC framework. For now, there is an emerging idea that understands consciousness as the ﬁnal result of unconsciousness processing. According to Hohwy (2013), perceptual consciousness ﬁts in the PC theory as the ‘upshot’ or ‘conclusion’ of unconscious perceptual inferences. Melloni (2014) also expects that inferential processes are conducted behind the curtain of consciousness and what we experience are the ‘outcomes’ or ‘results’ of an unconsciou inferential process. Lamme (2015) agrees with the idea that consciousness is based on the relation or more precisely conjunction of current inputs and priors, which together produce posterior beliefs. Karl Friston agrees to a certain extent with this interpretation of consciousness. According to Hobson and Friston (2016), consciousness is not a phenomenon but a process, a process of optimizing beliefs through inference (consciousness, dreams, and inference; the Cartesian theater revisited; a response to our theater critics).

@@

				@ \rewrite{Predictive inference and perception The concept of PC overturns classical notions of perception as a largely ‘bottom-up’ process of evidence accumulation or feature detection, proposing instead that perceptual content is speciﬁed by top-down predictive signals that emerge from hierarchically organized generative models of the causes of sensory signals. According to PC, the brain is continuously attempting to minimize the discrepancy or ‘prediction error’ between its inputs and its emerging models of the causes of these inputs via neural computations approximating Bayesian inference (Figure 1 and Box 1). Importantly, prediction errors can be minimized either by updating generative models (perceptual inference and learning; changing the model to ﬁt the world) or by performing actions to bring about sensory states in line with predictions (active inference; changing the world to ﬁt the model).}

@@

\rlstart{1}
		\subsection{Integrated information theory\needhelp{Help from Jun?}}
			\begin{ants}

>>>>

				@ \rewrite{
					It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig. 3, but the brain has no direct access to visual stimuli except that provided by the retina. Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs? More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + delta t in the future? The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +delta t j w t Þ } \url{http://tinyurl.com/y9zmhlln}

@@

		\subsection{Informational closure and level identification}

		\subsection{Biological Creature may try to achieve closure even the environment is not}

@@

\rlstart{3}	
		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
	    \ideaBox{I need to expend this section much more and more references}
	    In this section, we suggest that our theory has a strong exploratory and predictive power but with minimal assumptions.  
		Our theory indicates that, to make information conscious, a sufficient and a necessary conditions need to be satisfied.

		\begin{enumerate}
		    \item Sufficient condition: Information is encoded in NTIC process. 
		    \item Necessary condition: The system is capable of constructing NTIC processes at coarse-grained levels. 
		\end{enumerate}

@@

		    @ Boundary 
    		    @@ binocular rivalry/CFS
    		    @@ Libet's experiment
    		    @@ Unconscious determinants of free decisions in the human brain    		    
    		    @@ Priming
    		    @@ Bistable perception
    		    @@ Perceptual overflow
    		    @@ Threshold of unconscious to consciousness
    		    @@ Probabilistic information is always unconscious

@@

			\begin{WritingMaterials}
				@ \rewrite{
					The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations. Thus the crucial difference between the first-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity. Therefore, in the group of first-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the first-order representations, as well as scientists who hold that visual awareness depends on activity in content-specific regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26]. Most first-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g. subcortical) sensory pathways. Thus this view suggests that conscious and unconscious processing will have different functional consequences. Whereas some first-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most first-order theorists take a difference in perceptual task performance (e.g. ‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33]. In other words, they typically associate task performance with awareness..} \cite{lau2011empirical}

@@

			@ \rewrite{
				neutral about whether conscious awareness adds significant utility or immediate impact on behavior and task performance [1,27]. This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on first-order rather than higher-order representations. Because conscious awareness can differ even if all first-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
				\ideaCallout{
					My theory would have similar prediction. Because conscious contents are coarse-grained results from low-level information. It is possible that more than two low-level neural states all coarse-grained to a high-level state.  }

			@ \rewrite{
					Metacognition: cognition that is about another cognitive process as opposed to about objects in the world. In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efficacy of a perceptual process. The capacity of sensory metacognition is sometimes empirically assessed by the correspondence between subjective report and task performance: how closely are they associated with each other on a trial-by-trial basis}\cite{lau2011empirical}

@@

		Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates. In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process. This can cause a significant change of the brain states and resembles non-linear ignition of brain activities. Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing? Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness. A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly defined brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ]. Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be fiexibly deployed. \todo{Cite similar opinion from other theories}

@@

					@ e ‘all-or-none’ behavior, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and amplified non-linearly into a full-blown state of high-level activity. This global ‘ignition’ has been proposed as a marker of conscious perception [70]. Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear amplification of activation which invades a distributed set of parietal, prefrontal and cingulate areas
				\end{WritingMaterials}

@@

			\subsubsection{Ignition}
				\begin{WritingMaterials}
					@ Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing? Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness. A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly defined brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ]. Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be fiexibly deployed. 
				\end{WritingMaterials}

@@

				@ In their seminal article O’Regan and Noë (2001) introduce sensorimotor contingencies (SMCs) as the basis of a sensorimotor account of conscious perception.

@@

				@ The second variant of SMC theory postulates that ‘ it is not movement as such, but the consequences of potential movement that play a role ’ (in perceptual experience) ([5], p. 1015; see also [9,10,19,20]). This ‘ non-acute ’ or dispositional variant marks a signi fi cant shift in position because it de-emphasizes actual movement. \cite{pennartz2017consciousness}

@@

					@@ However, these authors have so far been very reticent about how exactly consciousness fits into the PC framework. For now, there is an emerging idea that understands consciousness as the final result of unconsciousness processing. According to Hohwy (2013), perceptual consciousness fits in the PC theory as the ‘upshot’ or ‘conclusion’ of unconscious perceptual inferences. Melloni (2014) also expects that inferential processes are conducted behind the curtain of consciousness and what we experience are the ‘outcomes’ or ‘results’ of an unconsciou inferential process. Lamme (2015) agrees with the idea that consciousness is based on the relation or more precisely conjunction of current inputs and priors, which together produce posterior beliefs. Karl Friston agrees to a certain extent with this interpretation of consciousness. According to Hobson and Friston (2016), consciousness is not a phenomenon but a process, a process of optimizing beliefs through inference (consciousness, dreams, and inference; the Cartesian theater revisited; a response to our theater critics).

@@

				@ \rewrite{Predictive inference and perception The concept of PC overturns classical notions of perception as a largely ‘bottom-up’ process of evidence accumulation or feature detection, proposing instead that perceptual content is specified by top-down predictive signals that emerge from hierarchically organized generative models of the causes of sensory signals. According to PC, the brain is continuously attempting to minimize the discrepancy or ‘prediction error’ between its inputs and its emerging models of the causes of these inputs via neural computations approximating Bayesian inference (Figure 1 and Box 1). Importantly, prediction errors can be minimized either by updating generative models (perceptual inference and learning; changing the model to fit the world) or by performing actions to bring about sensory states in line with predictions (active inference; changing the world to fit the model).}

@@

\rlstart{1}
		\subsection{Integrated information theory}
			\begin{ants}
